Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-06-27 2016-Weak-FH-Bisim/WeakBisim.tex
finish lemma 5

Thus, we can conclude: \TODO{que dire pour passer ici}\\
(\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\

>>>>

All the combinations of elements in $A$, $B$, and $C$ provides a set $X$ of weak open transitions (each combination of one transition in $A$, one in $B$, and one in $C$ provides one weak open transition in the set $X$, i.e. each $x\in X$ corresponds to a triple $(a,b,c)\in A\times B\times C$); this defines a set of weak open transitions indexed over $X$;  each such open transition leads to a $w_c$ that we call $t_x$. This re-indexing allows us to conclude:\\
$\Pred_{s,t} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} 
(\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
\qed
\end{proof}
